Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-05-25 R0V0.tex
Minor changes
Add 3D simulation without input and other minor changes

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTime}
	\caption{Time take by the parser to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

@@

\mypara The graph describing the network structure is provided in Figure~\ref{fig:graph}. As in the Section~\ref{sec:chain topology}, here same three scenarios are considered. Namely, the unconstrained case, the ``neighbor'' case and the fully decentralized case.

\begin{figure}[htpb!]
	\centering
	\input{./imgs/NewExample.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&48s\\
	Neighbor&57s\\
	Fully decentralized&43s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:mixed example}
\end{table}

>>>>

\mypara Figure~\ref{fig:3dsim} shows the $x$-component of a simulation of network~\eqref{eq:example} composed of three systems with the network structure as represented by the graph in Figure~\ref{fig:graph} and with input $u\equiv0$. Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\linewidth]{./imgs/3dsim.eps}
	\caption{Simulation of network~\eqref{eq:example} for 1s with input $u\equiv0$, $N=3$ and starting from random initial conditions.}
	\label{fig:3dsim}
\end{figure}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
	\caption{Time take by the parser to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

@@

\mypara The graph describing the network structure is provided in Figure~\ref{fig:cycle graph}. As in the Section~\ref{sec:chain topology}, here same three scenarios are considered. Namely, the unconstrained case, the ``neighbor'' case and the fully decentralized case.

\begin{figure}[htpb!]
	\centering
	\input{./imgs/NewExample.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:cycle graph}
\end{figure}

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&48s\\
	Neighbor&57s\\
	Fully decentralized&43s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:mixed example}
\end{table}
